---
title: "Factorial multivariate Bayesian causal forests with mvbcfMT"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Factorial multivariate Bayesian causal forests with mvbcfMT}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## The problem

Many studies expose each unit to *several* crossed binary treatments and record
*several* correlated outcomes. Estimating one treatment's average effect on one
outcome at a time discards two scientifically central quantities: how the
treatments **interact**, and how the effects **vary across units**. `mvbcfMT`
targets exactly this setting.

The model decomposes the factorial response surface over the treatment lattice,

$$
Y_i = \mu(x_i) + \sum_{\varnothing \neq S} \Big(\prod_{t \in S} Z_{it}\Big)\,\tau_S(x_i) + \varepsilon_i,
\qquad \varepsilon_i \sim N_q(0, \Sigma),
$$

into a prognostic forest $\mu$ plus one forest per main or interaction effect
$\tau_S$, all sharing the residual covariance $\Sigma$. A single unified sampler
draws every component.

## A worked example

```{r sim}
library(mvbcfMT)
sim <- simulate_multi(n = 300, p = 5, q = 2, Ti = 2, seed = 1)
head(sim$data[, c(sim$responses, sim$treatments)])
```

Fitting is a single call (kept small here so the vignette builds quickly; use
more iterations and trees in practice):

```{r fit, eval = FALSE}
fit <- fit_mvbcf_multi(
  sim$data,
  responses  = sim$responses,
  treatments = sim$treatments,
  covariates = sim$covariates,
  n_iter = 1000, n_burn = 500
)
```

## Estimands, honestly

The population **average** effect is the calibrated primary claim; per-unit
(CATE) surfaces are exploratory.

```{r effects, eval = FALSE}
## every main / interaction / joint effect with 95% credible intervals
predict_effects(fit, test = FALSE)

## one component's posterior effect surface
component_effect(fit, "tau_Z1:Z2", test = FALSE)
```

Before trusting any interaction, check that its factorial cell is populated. The
diagnostic flags thin cells as *unsupported*, not *null*:

```{r overlap, eval = FALSE}
overlap_diagnostic(fit)
```

## Debiased, doubly-robust average effects

`debiased_ate()` corrects the posterior-mean regime surfaces with a cross-fitted
augmented-IPW term over the factorial cells, giving semiparametric-efficient,
doubly-robust average effects with efficient standard errors and Wald intervals:

```{r debias, eval = FALSE}
debiased_ate(fit)
```

## Interpretability

Effects are rendered with value-suppressing uncertainty palettes, so cells with
diffuse posteriors recede to grey and no unsupported cell is over-read:

```{r vsup, eval = FALSE}
plot_effect_forest(fit)
plot_effect_vsup_xy(fit, "tau_Z1:Z2")
```
